sem

### 2023-02-09 scripts/workshop/sem.Rmd
use dev version of piecewiseSEM

@@

#fix error
#Error in data.frame(..., check.names = FALSE) :
#arguments imply differing number of rows: 0, 83
# sem <- psem(cc_temp, size_temp, prev_cc)
# sem_1 <- psem(cc_temp, size_temp, prev_temp_cc)
```

@@

shipley_psem3 <- psem(m1, m2, m3, m4)

#LLchisq(shipley_psem3)
```

>>>>

I fixed this error by installing the development version of piecewiseSEM

```{r}
#devtools::install_github("jslefche/piecewiseSEM@devel")
```

Caveat: GAMs can't be used for determining direct and indirect effects because these are not linear coefficients but rather smoothing terms.

@@

#fix error
#Error in data.frame(..., check.names = FALSE) :
#arguments imply differing number of rows: 0, 83
sem <- psem(cc_temp, size_temp, prev_cc)
sem_1 <- psem(cc_temp, size_temp, prev_temp_cc)
```

@@

shipley_psem3 <- psem(m1, m2, m3, m4)
#LLchisq(shipley_psem3)
```
